Adaptive Resolution Simulation in Equilibrium and Beyond

### 2015-02-25 writeDown/pub.epj/paper.tex
merge with Animeshs revise.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figs/system.alanine/system-region-1.eps}
  \caption{A schematic plot of an AdResS simulation. In side the red circle is the atomistic region. Between the red and blue circles is the hybrid region. Outside the blue circle is the coarse-grained region.}
  \label{fig:sys-region}
\end{figure}

In AdResS scheme, the simulation region $\Omega$ is 
decomposed without overlapping into three regions:
the atomistic region $\Omega_\AT$, the coarse-grained region $\Omega_\CG$, and
a hybrid region $\Omega_\HY$ bridging the former two regions.
That means the atomistic region is always connected to the coarse-grained region via a hybrid region.
The names of the atomistic and coarse-grained regions are self-explanatory, while
in the hybrid region each molecule has both the atomistic and coarse-grained resolutions.
A schematic plot of an AdResS simulation is presented in Fig.~\ref{fig:sys-region}.
The AdResS uses a scalar weighting function $w(\vect r),\ \vect r\in\Omega$ 
to denote the resolution of the molecule at position $\vect r$.
% In the atomistic region the value of the
% weighting function is usually set to 1, while in the coarse-grained
% region it is usually set to 0. In between, there is a bybrid region
% that is denoted by $\Omega_\HY$
% (or called transition region), where the molecules
% has both the atomistic and coarse-grained resolutions, and the weighting function
% goes smoothly from 1 to 0.
The definition of the weighting function
is not unique, one possible and perhaps the most popular choice is
\begin{equation}\label{eqn:old-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT)}{d_\HY}\,\Big] && \vect r \in\Omega_\HY \\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
where $\dist(\vect r, \Omega_\AT)$ is the distance between the
position $\vect r$ and the atomistic region, which is defined
by $\dist(\vect r, \Omega_\AT) = \min_{\vect s\in\Omega_\AT} \vert
\vect r - \vect s \vert$.  $d_\HY$ is the thickness of the hybrid
region. We always assume the thickness of the hybrid region to be
uniform, which indicates that the weighting function smoothly vanishes
at the boundary between the hybrid and the coarse-grained regions.
AdResS requires 
all interactions\footnote{The long-range electrostatic interactions
  are also treated by the cut-off method. \recheck{It is possible by using e.g.~the Reaction-Field method~\cite{onsager1936electric,tironi1995generalized}
  to calculate the electrostatic interactions.}
} being treated
by the cut-off method\footnote{\recheck{AdResS uses the same general cut-off method as in normal MD simulations~\cite{frenkel2001understanding}.}}, and the thickness of
the hybrid region being at least one cut-off radius (denoted by $r_c$).
Moreover, owing to the double-resolution of hybrid molecules,
an atomistic molecule only interacts with the 
atomistic resolution of a hybrid molecule,
while a coarse-grained molecule only interacts with the coarse-grained resolution
of a hybrid molecule.
The atomistic molecules are thus not directly interacting with the coarse-grained molecules.
The benefit of these settings is that
there is no extra work for modeling the cross-scale interactions.

The intermolecular interactions are
well defined in the atomistic and coarse-grained regions by the corresponding models.
To setup an AdResS simulation, one only needs to define the
interactions in the hybrid region. There are in general two
possibilities: force interpolation and the potential interpolation.
The force interpolation approach defines the hybrid force between two
molecules (indexed by $\moleidxone$ and $\moleidxtwo$) by a linear interpolation
between the atomistic (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\AT}$) and coarse-grained (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\CG}$) forces.
\begin{align}\label{eqn:f-f-interpol}
  {\vect F}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo} 
\end{align}
where $w_\moleidxone = w(\vect r_\moleidxone)$ is the weighting function
measured at the center-of-mass (COM) position of molecule $\moleidxone$.
It should be noted that the AdResS  force interpolation is not conservative, i.e.~there does not
exist a potential so that the force interpolation is derived by taking the negative gradient of the potential,
unless the coarse-grained interaction is identical to the atomistic interaction~\cite{praprotnik2011comment,dellesite2007some}.
It is easy to show that the force interpolation satisfies the momentum conservation: Since
both the atomistic and coarse-grained forces are subject to the Newton's third law, i.e.~${\vect F}_{\moleidxone\moleidxtwo}^{\AT} = - {\vect F}_{\moleidxtwo\moleidxone}^{\AT}$
and ${\vect F}_{\moleidxone\moleidxtwo}^{\CG} = - {\vect F}_{\moleidxtwo\moleidxone}^{\CG}$. From the definition Eq.~\eqref{eqn:f-f-interpol} we have ${\vect F}_{\moleidxone\moleidxtwo} = - {\vect F}_{\moleidxtwo\moleidxone}$.

@@

\begin{table}
  \centering
  \caption{A summary of the fundamental conservation laws in mechanics 
    satisfied by the normal molecular system and AdResS systems defined by force and potential interpolations.}
  \label{tab:conv-laws}
  \begin{tabular*}{0.8\textwidth}{@{\extracolsep{\fill}}lcc}\hline\hline
    &         Momentum Consv.     &       Energy Consv. \\
    Normal molecular System     &       {Yes}        &       {Yes}\\      
    AdResS force interpol.   &       {Yes}        &       {No}\\      
    AdResS potential interpol.  &     {No}  &       {Yes}\\\hline\hline
  \end{tabular*}
\end{table}
The fundamental conservation laws satisfied by both the force and potential interpolations
are summarized in Tab.~\ref{tab:conv-laws}. Unlike normal molecular systems, in which both
the momentum and energy are conserved, neither of the AdResS systems conserves
both laws. The breaking of these mechanics conservations has substantial influence on the thermodynamic
properties of the AdResS systems (see the discussions in Sec.~\ref{sec:thermodynamic}).
% The choice of the interpolation scheme depends on
% the practical requirement, for example, in hydrodynamic systems it is crucial to have the momentum
% conservation, then the force interpolation is prefered.
Regarding the equilibrium statistical properties, we will show later in Sec.~\ref{sec:statistical}
that both approaches approximately sample the grand-canonical ensemble.

When the intermolecular force is defined by either
Eq.~\eqref{eqn:f-f-interpol} or \eqref{eqn:f-v-interpol}, the total
force exerts on one molecule is the sum of all pairwise forces:
\begin{align}
  \vect F_\moleidxone = \sum_\moleidxtwo \vect F_{\moleidxone\moleidxtwo}, \quad \vect F^V_\moleidxone = \sum_\moleidxtwo \vect F^V_{\moleidxone\moleidxtwo}
\end{align}
The force on the atomistic degrees of freedom (DOFs) of a hybrid molecule is distributed 
by, 
\begin{align}
  \vect F_\atomidxone = \frac{m_\atomidxone}{M_\moleidxone}\vect F_\moleidxone, \quad   \vect F^V_\atomidxone = \frac{m_\atomidxone}{M_\moleidxone}\vect F^V_\moleidxone 
\end{align}
where  $\atomidxone$ is the index of an atom in molecule $\moleidxone$.
$m_\atomidxone$ is the mass of atom $\alpha$, and $M_\moleidxone$ is the total mass of molecule $\moleidxone$, i.e.~$M_\moleidxone = \sum_{\atomidxone\in\moleidxone}m_\atomidxone$.

@@

In order to consider the accuracy of the AdResS from a statistical perspective, we always compare it with a full
atomistic reference system, which is of the same size as the AdResS system,
and contains the same number of molecules.
If the configuration of the atomistic region in the AdResS 
is the same as that of the corresponding subregion in the atomistic reference, then
the AdResS  is of good accuracy (see the comparison indicated by the red arrow in Fig.~\ref{fig:compare}).
A well-known conclusion of the standard statistical mechanics is that
when the reference system approximates the thermodynamic limit, the subsystem
\recheck{samples} the grand-canonical ensemble. Therefore, it is natural to investigate
if the atomistic region of AdResS also \recheck{samples} the grand-canonical ensemble
in the same thermodynamic limit. The theoretical framework presented in this section works for
both the force and potential interpolations.

@@

We denote the number of molecules, volume and temperature of the system by $N$, $V$ and $T$, respectively.
The atomistic reference system has exactly the same set of variables, and its equilibrium state  is
the \emph{desired equilibrium} of AdResS.
% The word ``desired'' means that
% the atomistic region of the AdResS system should reproduce the equilibrium properties corresponding subregion of the reference
% system.
The thermodynamic variables of the subregions are specified by the subscript,
for example, those of the atomistic region are 
$N_\AT$, $V_\AT$ and $T_\AT$. Those of the hybrid and coarse-grained regions
are denoted by adding subscripts ``$\HY$'' and ``$\CG$'', respectively.
Identities $N = N_\AT + N_\HY + N_\CG$ and $V = V_\AT + V_\HY + V_\CG$ obviously hold
in the AdResS system.
In equilibrium, the temperature is uniform across the system: $T = T_\AT = T_\HY = T_\CG$.
This is achieved in practice by coupling the whole system to a Langevin thermostat.
The pressure and chemical potential of the atomistic and coarse-grained regions
are denoted by $\{p_\AT, \mu_\AT\}$
and $\{p_\CG, \mu_\CG\}$, respectively.
The DOFs of molecules indexed $\moleidxone$ are $\vect x_\moleidxone = \{\vect r_\moleidxone, \vect p_\moleidxone\}$, where
$\vect r_\moleidxone$ denotes the generalized coordinates and $\vect p_\moleidxone$ denotes the corresponding momenta.
All the DOFs of the system are denoted by $\vect x = \{\vect x_1, \cdots, \vect x_N\}$. Without loss of
generality, we consider that molecules index by $\{1, \cdots, N_\AT\}$ are in the atomistic region, then $\{N_\AT+1, \cdots, N_\AT + N_\HY\}$ are in the hybrid region, and
the last $N_\CG$ molecules $\{N-N_\CG+1, \cdots, N\}$ are in the coarse-grained region. The corresponding DOFs are denoted by $\vect x_\AT$, $\vect x_\HY$ and $\vect x_\CG$.
It should be noted that for simplicity, we do not explicitly consider that the number of DOFs are different for an atomistic
and a coarse-grained molecule, and uniformly encode them by the vector $\vect x$.
% so it is acutally 
% \redc{The atomistic, hybrid and coarse-grained have different DOFs, a comment needed!}

@@

In practice, the density in the hybrid region is corrected by the
thermodynamic force~\cite{fritsch2012adaptive}, which is applied on top of the AdResS intermolecular interactions:
\begin{align}\label{eqn:thf-f}
  \vect F_\moleidxone &= \sum_\moleidxtwo \vect F_{\moleidxone\moleidxtwo}  + \vect F_\moleidxone^\thf,  \\\label{eqn:thf-p}
  \vect F^V_\moleidxone& = \sum_\moleidxtwo \vect F^V_{\moleidxone\moleidxtwo} + \vect F_\moleidxone^{\thf,V},
\end{align}
where the thermodynamic forces is a one-body force defined over space,
i.e.~$\vect F^\thf_i = \vect F^\thf(\vect r_\moleidxone)$ and $\vect F^{\thf, V}_\moleidxone = \vect F^{\thf,V}(\vect r_\moleidxone)$,
for force and potential interpolations, respectively.
The thermodynamic force is applied only in the hybrid region, and is
calculated by the following iterative scheme:
\begin{align}\label{eqn:tfi}
  \vect F_{k+1}^{\thf(, V)} (\vect r) = \vect F_k^{\thf(, V)} (\vect r)-
  \frac{M}{\kappa(\rho^\ast_\AT)^2} \nabla\rho_k(\vect r)
\end{align}
where $k$ denotes the step of iteration and $\kappa$ is the
isothermal-compressibility. In equilibrium the density profile $\rho(\vect r)$ in the
atomistic and coarse-grained regions are constants, so the thermodynamic force
is updated only in the hybrid region. When the hybrid density is flat, the thermodynamic
force converges. An important consequence is that
\begin{align}
  \rho_\AT(\vect r) = \rho_\HY(\vect r) = \rho_\CG(\vect r) = \rho_\AT^\ast,
\end{align}
because the density profiles match at the atomistic-hybrid and
hybrid-coarse-grained boundaries.

@@

From the analysis on statistical mechanics, one surprising fact is that if the
requirement for the accuracy is not very high (only applying the
thermodynamic force is acceptable), then there is actually no
restriction on the coarse-grained model. One can even use ideal gas as
a coarse-grained model.  The computational difficulty lies in the
sudden switching-on of the atomistic interactions when a coarse-grained
molecule enters the hybrid region. If two molecules enter at
the same time and the same location, then the atomistic contribution
to the intermolecular interaction
% ~\eqref{eqn:f-f-interpol} or
% \eqref{eqn:f-v-interpol}
is infinity, which drives the simulation
unstable. This numerical difficulty can be avoided by using capped
atomistic interaction~\cite{praprotnik2005adaptive}, or by using a
gradually switching-on core-softened atomistic
interaction~\cite{heyes2010thermodynamic}.
In Ref.~\cite{wang2013grand}, the authors instead tested with
Weeks-Chandler-Andersen (WCA) potential~\cite{weeks1971role} as the
coarse-grained model, which is a short-ranged and pure repulsive
interaction.  For an SPC/E water system, the cut-off radius of WCA potential
can be 2.4 time smaller than the cut-off radius used in the atomistic
region. Since the computational cost of cut-off scheme is of order $\mo(r_c^3)$,
the pair interaction of WCA
is 19 times cheaper. Moreover, for each pair of molecules the atomistic model computes
10 pairwise interactions (9 electrostatic + 1 van der Waals), while the
WCA model computes only one. Therefore the WCA model in total costs only $1/190$ 
on force computation than the SPC/E atomistic model.
The WCA approach has been successfully used in calculating the
chemical potential of various complex fluids and mixtures~\cite{agarwal2014chemical}.

@@

The alanine dipeptide molecule (see Fig.~\ref{fig:ala}~(a)) is usually
used as a testing case for evaluating the new computational method in simulating 
biomolecular system (see e.g.~Ref.~\cite{apostolakis1999calculation,chodera2007automatic,kaminsky2007force,gfeller2007complex}).
We investigate a system composed of
7235 TIP3P water molecules, and
one alanine dipeptide described by the CHARMM27 force field~\cite{foloppe2000all} with
grid-based energy correction map (CMAP)~\cite{mackerell2004extending}. 
The dimension of the simulation region is $6.1\times6.1\times6.1~\textrm{nm}^3$, which is divided into
a spherical atomistic region of radius  $0.5$~nm centered at the $\alpha$-carbon and a  shell-shaped hybrid region of width 2.0~nm.
The rest of the system is treated coarse-grainly by the WCA interaction.
The dynamical region  is
also centered at the $\alpha$-carbon, and is of radius 1.2~nm.
It has been proved that the conformational dynamics of alanine dipeptide is not sensitive to the size of
the dynamical region when the radius is larger than 1.0~nm~\cite{wang2014exploring}.
In this case, part of the hybrid region is not thermostated, so
when using force interpolation, the extra energy production might not be effectively equilibriated.
To this end, we only investigate the potential interpolation. The corresponding
thermodynamic force is iteratively computed by
Eq.~\eqref{eqn:tfi}.
The electrostatic interaction is computed by the Reaction-Field method with dielectric constant $\varepsilon_{\textrm{rf}} = +\infty$.
Both the electrostatic and the van der Waals interactions (smoothed by ``\texttt{switch}'' method in Gromacs)
are cut-off at 1.0~nm.

@@

If one were able to answer the questions regarding the accuracy of the equilibrium
ensemble of AdResS, the accuracy of quantities that are equilibrium ensemble
averages would be automatically answered. However, the dynamical properties, which are
not equilibrium ensemble averages, are out of the scope of the 
GC-AdResS framework. In order to numerically check the accuracy of AdResS
in computing the dynamical properties, we investigated the velocity auto-correlation
function of pure water and the leading relaxation time-scales of alanine dipeptide
dissolved in water.
The significant time-scale of the time-correlations ranges from 1~ps in the case of velocity auto-correlation
to almost 600~ps in the case of conformational relaxation of alanine dipeptide.
In both systems the AdResS reproduces the atomistic result
with a satisfactory agreement.
Although these positive numerically evidences cannot answer the open questions
on the reason behind the high accuracy, nor the error estimates of the dynamical properties,
they are strong evidence on the applicability of AdResS beyond equilibrium simulations,
and suggests a direction for theoretical investigations.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figs/system.alanine/system-region-1.eps}
  \caption{A schematic plot of an AdResS simulation. Inside the red circle is the atomistic region. Between the red and blue circles is the hybrid region. Outside the blue circle is the coarse-grained region.}
  \label{fig:sys-region}
\end{figure}

In AdResS scheme, the simulation region $\Omega$ is 
decomposed without overlapping into three regions:
the atomistic region $\Omega_\AT$, the coarse-grained region $\Omega_\CG$, and
a hybrid region $\Omega_\HY$ bridging the former two regions.
That means the atomistic region is always connected to the coarse-grained region via a hybrid region.
The names of the atomistic and coarse-grained regions are self-explanatory, while
in the hybrid region each molecule has both the atomistic and coarse-grained resolutions.
A schematic plot of an AdResS simulation is presented in Fig.~\ref{fig:sys-region}.
AdResS uses a scalar weighting function $w(\vect r),\ \vect r\in\Omega$ 
to denote the resolution of the molecule at position $\vect r$.
% In the atomistic region the value of the
% weighting function is usually set to 1, while in the coarse-grained
% region it is usually set to 0. In between, there is a bybrid region
% that is denoted by $\Omega_\HY$
% (or called transition region), where the molecules
% has both the atomistic and coarse-grained resolutions, and the weighting function
% goes smoothly from 1 to 0.
The definition of the weighting function
is not unique, one possible and perhaps the most popular choice is
\begin{equation}\label{eqn:old-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT)}{d_\HY}\,\Big] && \vect r \in\Omega_\HY \\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
where $\dist(\vect r, \Omega_\AT)$ is the distance between the
position $\vect r$ and the atomistic region, which is defined
by $\dist(\vect r, \Omega_\AT) = \min_{\vect s\in\Omega_\AT} \vert
\vect r - \vect s \vert$.  $d_\HY$ is the thickness of the hybrid
region. We always assume the thickness of the hybrid region to be
uniform, which indicates that the weighting function smoothly vanishes
at the boundary between the hybrid and the coarse-grained regions.
AdResS requires 
all interactions\footnote{The long-range electrostatic interactions
  are also treated by the cut-off method. \recheck{It is possible by using e.g.~the Reaction-Field method~\cite{onsager1936electric,tironi1995generalized}
  to calculate the electrostatic interactions.}
} being treated
by the cut-off method\footnote{\recheck{AdResS uses the same general cut-off method as in normal MD simulations~\cite{frenkel2001understanding}.}}, and the thickness of
the hybrid region being at least one cut-off radius (denoted by $r_c$).
Moreover, owing to the double-resolution of hybrid molecules,
an atomistic molecule only interacts with the 
atomistic resolution of a hybrid molecule,
while a coarse-grained molecule only interacts with the coarse-grained resolution
of a hybrid molecule.
The atomistic molecules are thus not directly interacting with the coarse-grained molecules.
The benefit of these settings is that
there is no extra work for modeling the cross-scale interactions.

The intermolecular interactions are
well defined in the atomistic and coarse-grained regions by the corresponding models.
To set up an AdResS simulation, one only needs to define the
interactions in the hybrid region. There are in general two
possibilities: force interpolation and the potential interpolation.
The force interpolation approach defines the hybrid force between two
molecules (indexed by $\moleidxone$ and $\moleidxtwo$) by a linear interpolation
between the atomistic (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\AT}$) and coarse-grained (denoted by ${\vect F}_{\moleidxone\moleidxtwo}^{\CG}$) forces.
\begin{align}\label{eqn:f-f-interpol}
  {\vect F}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo} 
\end{align}
where $w_\moleidxone = w(\vect r_\moleidxone)$ is the weighting function
measured at the center-of-mass (COM) position of molecule $\moleidxone$.
It should be noted that the AdResS  force interpolation is not conservative, i.e.~there does not
exist a potential so that the force interpolation is derived by taking the negative gradient of the potential,
unless the coarse-grained interaction is identical to the atomistic interaction~\cite{praprotnik2011comment,dellesite2007some}.
It is easy to show that the force interpolation satisfies the momentum conservation: Since
both the atomistic and coarse-grained forces are subject to the Newton's third law, i.e.~${\vect F}_{\moleidxone\moleidxtwo}^{\AT} = - {\vect F}_{\moleidxtwo\moleidxone}^{\AT}$
and ${\vect F}_{\moleidxone\moleidxtwo}^{\CG} = - {\vect F}_{\moleidxtwo\moleidxone}^{\CG}$. From the definition Eq.~\eqref{eqn:f-f-interpol} we have ${\vect F}_{\moleidxone\moleidxtwo} = - {\vect F}_{\moleidxtwo\moleidxone}$.

@@

\begin{table}
  \centering
  \caption{A summary of the fundamental conservation laws in mechanics 
    satisfied by the normal molecular system and AdResS systems defined by force and potential interpolations.}
  \label{tab:conv-laws}
  \begin{tabular*}{0.8\textwidth}{@{\extracolsep{\fill}}lcc}\hline\hline
    &         Momentum Consv.     &       Energy Consv. \\
    Normal molecular System     &       {Yes}        &       {Yes}\\      
    AdResS force interpol.   &       {Yes}        &       {No}\\      
    AdResS potential interpol.  &     {No}  &       {Yes}\\\hline\hline
  \end{tabular*}
\end{table}
The fundamental conservation laws satisfied by both the force and potential interpolations
are summarized in Tab.~\ref{tab:conv-laws}. Unlike normal molecular systems, in which both
the momentum and energy are conserved, neither of the AdResS systems conserves
both laws. The violation of these mechanical conservation laws has substantial influence on the thermodynamic
properties of the AdResS systems (see the discussions in Sec.~\ref{sec:thermodynamic}).
% The choice of the interpolation scheme depends on
% the practical requirement, for example, in hydrodynamic systems it is crucial to have the momentum
% conservation, then the force interpolation is prefered.
Regarding the equilibrium statistical properties, we will show later in Sec.~\ref{sec:statistical}
that both approaches approximately sample the grand-canonical ensemble.

When the intermolecular force is defined by either
Eq.~\eqref{eqn:f-f-interpol} or \eqref{eqn:f-v-interpol}, the total
force exerted on one molecule is the sum of all pairwise forces:
\begin{align}
  \vect F_\moleidxone = \sum_\moleidxtwo \vect F_{\moleidxone\moleidxtwo}, \quad \vect F^V_\moleidxone = \sum_\moleidxtwo \vect F^V_{\moleidxone\moleidxtwo}
\end{align}
The force on the atomistic degrees of freedom (DOFs) of a hybrid molecule is distributed 
by, 
\begin{align}
  \vect F_\atomidxone = \frac{m_\atomidxone}{M_\moleidxone}\vect F_\moleidxone, \quad   \vect F^V_\atomidxone = \frac{m_\atomidxone}{M_\moleidxone}\vect F^V_\moleidxone 
\end{align}
where  $\atomidxone$ is the index of an atom in molecule $\moleidxone$.
$m_\atomidxone$ is the mass of atom $\alpha$, and $M_\moleidxone$ is the total mass of molecule $\moleidxone$, i.e.~$M_\moleidxone = \sum_{\atomidxone\in\moleidxone}m_\atomidxone$.

@@

In order to consider the accuracy of the AdResS from a statistical perspective, we always compare it with a full
atomistic reference system, which is of the same size as the AdResS system,
and contains the same number of molecules.
If the configuration of the atomistic region in AdResS 
is same as that of the corresponding subregion in the atomistic reference, then
AdResS is of good accuracy (see the comparison indicated by the red arrow in Fig.~\ref{fig:compare}).
A well-known conclusion of the standard statistical mechanics is that
when the reference system approximates the thermodynamic limit, the subsystem
\recheck{samples} the grand-canonical ensemble. Therefore, it is natural to investigate
if the atomistic region of AdResS also \recheck{samples} the grand-canonical ensemble
in the same thermodynamic limit. The theoretical framework presented in this section works for
both the force and potential interpolations.

@@

We denote the number of molecules, volume and temperature of the system by $N$, $V$ and $T$, respectively.
The atomistic reference system has exactly the same set of variables, and its equilibrium state  is
the \emph{desired equilibrium} of AdResS.
% The word ``desired'' means that
% the atomistic region of the AdResS system should reproduce the equilibrium properties corresponding subregion of the reference
% system.
The thermodynamic variables of the subregions are specified by the subscript,
for example, those of the atomistic region are 
$N_\AT$, $V_\AT$ and $T_\AT$ and those of the hybrid and coarse-grained regions
are denoted by adding subscripts ``$\HY$'' and ``$\CG$'', respectively.
Identities $N = N_\AT + N_\HY + N_\CG$ and $V = V_\AT + V_\HY + V_\CG$ obviously hold
in the AdResS system.
In equilibrium, the temperature is uniform across the system: $T = T_\AT = T_\HY = T_\CG$.
This is achieved in practice by coupling the whole system to a Langevin thermostat.
The pressure and chemical potential of the atomistic and coarse-grained regions
are denoted by $\{p_\AT, \mu_\AT\}$
and $\{p_\CG, \mu_\CG\}$, respectively.
The DOFs of molecules indexed $\moleidxone$ are $\vect x_\moleidxone = \{\vect r_\moleidxone, \vect p_\moleidxone\}$, where
$\vect r_\moleidxone$ denotes the generalized coordinates and $\vect p_\moleidxone$ denotes the corresponding momenta.
All the DOFs of the system are denoted by $\vect x = \{\vect x_1, \cdots, \vect x_N\}$. Without loss of
generality, we consider that molecules index by $\{1, \cdots, N_\AT\}$ are in the atomistic region, then $\{N_\AT+1, \cdots, N_\AT + N_\HY\}$ are in the hybrid region, and
the last $N_\CG$ molecules $\{N-N_\CG+1, \cdots, N\}$ are in the coarse-grained region. The corresponding DOFs are denoted by $\vect x_\AT$, $\vect x_\HY$ and $\vect x_\CG$.
It should be noted that for simplicity, we do not explicitly consider that the number of DOFs are different for an atomistic
and a coarse-grained molecule, and uniformly encode them by the vector $\vect x$.
% so it is acutally 
% \redc{The atomistic, hybrid and coarse-grained have different DOFs, a comment needed!}

@@

In practice, the density in the hybrid region is corrected by the
thermodynamic force~\cite{fritsch2012adaptive}, which is applied on top of the AdResS intermolecular interactions:
\begin{align}\label{eqn:thf-f}
  \vect F_\moleidxone &= \sum_\moleidxtwo \vect F_{\moleidxone\moleidxtwo}  + \vect F_\moleidxone^\thf,  \\\label{eqn:thf-p}
  \vect F^V_\moleidxone& = \sum_\moleidxtwo \vect F^V_{\moleidxone\moleidxtwo} + \vect F_\moleidxone^{\thf,V},
\end{align}
where the thermodynamic force is a one-body force defined over space,
i.e.~$\vect F^\thf_i = \vect F^\thf(\vect r_\moleidxone)$ and $\vect F^{\thf, V}_\moleidxone = \vect F^{\thf,V}(\vect r_\moleidxone)$,
for force and potential interpolations, respectively.
The thermodynamic force is applied only in the hybrid region, and is
calculated by the following iterative scheme:
\begin{align}\label{eqn:tfi}
  \vect F_{k+1}^{\thf(, V)} (\vect r) = \vect F_k^{\thf(, V)} (\vect r)-
  \frac{M}{\kappa(\rho^\ast_\AT)^2} \nabla\rho_k(\vect r)
\end{align}
where $k$ denotes the step of iteration and $\kappa$ is the
isothermal-compressibility. In equilibrium the density profile $\rho(\vect r)$ in the
atomistic and coarse-grained regions are constants, so the thermodynamic force
is updated only in the hybrid region. When the density in hybrid region is flat, the thermodynamic
force converges. An important consequence is that
\begin{align}
  \rho_\AT(\vect r) = \rho_\HY(\vect r) = \rho_\CG(\vect r) = \rho_\AT^\ast,
\end{align}
because the density profiles match at the atomistic-hybrid and
hybrid-coarse-grained boundaries.

@@

From the analysis on statistical mechanics, one surprising fact is that if the
requirement for the accuracy is not very high (only applying the
thermodynamic force is acceptable), then there is actually no
restriction on the coarse-grained model. One can even use ideal gas as
a coarse-grained model.  The computational difficulty lies in the
sudden switching-on of the atomistic interactions when a coarse-grained
molecule enters the hybrid region. If two molecules enter at
the same time and the same location, then the atomistic contribution
to the intermolecular interaction
% ~\eqref{eqn:f-f-interpol} or
% \eqref{eqn:f-v-interpol}
is infinity, which drives the simulation
unstable. This numerical difficulty can be avoided by using capped
atomistic interaction~\cite{praprotnik2005adaptive}, or by using a
gradually switching-on core-softened atomistic
interaction~\cite{heyes2010thermodynamic}.
In Ref.~\cite{wang2013grand}, the authors instead tested 
Weeks-Chandler-Andersen (WCA) potential~\cite{weeks1971role} as the
coarse-grained potential, which is a short-ranged and pure repulsive
interaction.  For an SPC/E water system, the cut-off radius of WCA potential
can be 2.4 times smaller than the cut-off radius used in the atomistic
region. Since the computational cost of cut-off scheme is of order $\mo(r_c^3)$,
the pair interaction of WCA
is 19 times cheaper. Moreover, for each pair of molecules the atomistic model computes
10 pairwise interactions (9 electrostatic + 1 van der Waals), while the
WCA model computes only one. Therefore the WCA model in total costs only $1/190$ 
on force computation than the SPC/E atomistic model.
The WCA approach has been successfully used in calculating the
chemical potential of various complex fluids and mixtures~\cite{agarwal2014chemical}.

@@

The alanine dipeptide molecule (see Fig.~\ref{fig:ala}~(a)) is usually
used as a testing case for evaluating the new computational method in simulating 
biomolecular system (see e.g.~Ref.~\cite{apostolakis1999calculation,chodera2007automatic,kaminsky2007force,gfeller2007complex}).
We investigate a system composed of
7235 TIP3P water molecules, and
one alanine dipeptide described by the CHARMM27 force field~\cite{foloppe2000all} with
grid-based energy correction map (CMAP)~\cite{mackerell2004extending}. 
The dimension of the simulation region is $6.1\times6.1\times6.1~\textrm{nm}^3$, which is divided into
a spherical atomistic region of radius  $0.5$~nm centered at the $\alpha$-carbon and a  shell-shaped hybrid region of width 2.0~nm.
The rest of the system is coarse-grained by the WCA interaction.
The dynamical region  is
also centered at the $\alpha$-carbon, and is of radius 1.2~nm.
It has been proven that the conformational dynamics of alanine dipeptide is not sensitive to the size of
the dynamical region when the radius is larger than 1.0~nm~\cite{wang2014exploring}.
In this case, part of the hybrid region is not thermostated, so
when using force interpolation, the extra energy production might not be effectively equilibriated.
To this end, we only investigate the potential interpolation. The corresponding
thermodynamic force is iteratively computed by
Eq.~\eqref{eqn:tfi}.
The electrostatic interaction is computed by the Reaction-Field method with dielectric constant $\varepsilon_{\textrm{rf}} = +\infty$.
Both the electrostatic and the van der Waals interactions (smoothed by ``\texttt{switch}'' method in Gromacs)
are treated using cut-off scheme. The cut-off used in both the cases is 1.0~nm.

@@

If one were able to answer the questions regarding the accuracy of the equilibrium
ensemble of AdResS, the accuracy of quantities that are equilibrium ensemble
averages would be automatically answered. However, the dynamical properties, which are
not equilibrium ensemble averages, are out of the scope of the 
GC-AdResS framework. In order to numerically check the accuracy of AdResS
in computing the dynamical properties, we investigated the velocity auto-correlation
function of pure water and the leading relaxation time-scales of alanine dipeptide
dissolved in water.
The significant time-scale of the time-correlations ranges from 1~ps in the case of velocity auto-correlation
to almost 600~ps in the case of conformational relaxation of alanine dipeptide.
In both systems the AdResS reproduces the atomistic result
with a satisfactory agreement.
Although these positive numerical evidences can neither answer the open questions
on the reason behind the high accuracy, nor the error estimates of the dynamical properties,
they are strong evidence on the applicability of AdResS beyond equilibrium simulations,
and suggest a direction for theoretical investigations.
